### 2021-11-17 README.Rmd
update 2021-11-17 15:21:16

For most users, the recommended starting point is to [read the paper](https://osf.io/zcvbs/), currently in press in [Data Science](https://content.iospress.com/journals/data-science/Pre-press/Pre-press),
which introduces the WORCS workflow, explains the underlying tools, and illustrates how the `worcs` package can be used to create a new project that follows the workflow.

@@

> Van Lissa, C. J., Brandmaier, A. M., Brinkman, L., Lamprecht, A., Peikert, A., , Struiksma, M. E., & Vreede, B. (in press). WORCS: A Workflow for Open Reproducible Code in Science. Data Science, in press. https://doi.org/10.17605/OSF.IO/ZCVBS

@@

1. The preprint has been downloaded 776 times, since being published on 31-05-2020 (currently in press in [Data Science](https://content.iospress.com/journals/data-science/Pre-press/Pre-press))
1. The `worcs` R-package has been downloaded `r dl` times from CRAN, since being published on 18-05-2020
1. The GitHub project has been forked `r worcs_repo$network_count` times, watched `r worcs_repo$subscribers_count` times, and starred `r worcs_repo$watchers` times
1. The lead author has given invited lectures on WORCS at:`r invited`
1. WORCS is currently used in the following GitHub repositories (sorted by user):`r tmp`

>>>>

For most users, the recommended starting point is to [read the paper, published in Data Science](https://content.iospress.com/articles/data-science/ds210031),
which introduces the WORCS workflow, explains the underlying tools, and illustrates how the `worcs` package can be used to create a new project that follows the workflow.

@@

> Van Lissa, C. J., Brandmaier, A. M., Brinkman, L., Lamprecht, A., Peikert, A., , Struiksma, M. E., & Vreede, B. (in press). WORCS: A Workflow for Open Reproducible Code in Science. Data Science, 2021. Data Science, vol. 4, no. 1, pp. 29-49. DOI: 10.3233/DS-210031.

@@

1. The preprint has been downloaded 1372 times, since being published on 31-05-2020
1. The paper in [Data Science](https://content.iospress.com/articles/data-science/ds210031) has been cited 13 times
1. The `worcs` R-package has been downloaded `r dl` times from CRAN, since being published on 18-05-2020
1. The GitHub project has been forked `r worcs_repo$network_count` times, watched `r worcs_repo$subscribers_count` times, and starred `r worcs_repo$watchers` times
1. The lead author has given invited lecturegs on WORCS at:`r invited`
1. WORCS is currently used in the following public itHub repositories (sorted by user):`r tmp`
